Medical Concept Extraction

### 2012-12-14 paper/paper.tex
Fixes to the paper.
Progress on paper

\numberofauthors{3}
\author{
\alignauthor
Samantha Ainsley\\
\affaddr{MIT EECS}
\email{ainsley@mit.edu}
\alignauthor
Salman Ahmad\\
\affaddr{MIT EECS}
\email{saahmad@mit.edu}
\alignauthor
Tristan Naumann\\
\affaddr{MIT EECS}
\email{tjn@mit.edu}
}

@@

\section{Introduction}
\label{sec:introduction}

@@

\section{Acknowledgments}
\label{sec:acknowledgments}

>>>>

\numberofauthors{3}
\author{
\alignauthor
Tristan Naumann\\
\affaddr{MIT EECS}
\email{tjn@mit.edu}
\alignauthor
Samantha Ainsley\\
\affaddr{MIT EECS}
\email{ainsley@mit.edu}
\alignauthor
Salman Ahmad\\
\affaddr{MIT EECS}
\email{saahmad@mit.edu}
}

@@

\section{Introduction}

@@

\section{Related Work}

\vspace{1in}

\section{Machine Learning}

Talk about multi-class classification

\subsection{Support Vector Machines}

\subsection{Linear Regression}

\subsection{Conditional Random Fields}

\vspace{1in}

\section{Domain Specific Challenges}

\subsection{Sparse Data}

\vspace{1in}

\section{Algorithm}

\subsection{Sentence Features}

\subsection{Word Features}

Call out importance of word shape

\subsection{Dimension Compression}

\subsection{n-gram Features}

\subsection{Parameter Tuning}

\begin{itemize}

\item Grid search and grid search image

\item Cross validation

\end{itemize}

\section{System}

\subsection{Code Architecture}

Include a system diagram of the code base.

Discuss and cite LIBSVM, LIBLINEAR and CRFSUITE.

\subsection{Web Service}

Where we can see the system running live.

\section{Results}

\subsection{Data Set}

Talk about the competition and where the data came from. How large the data size is, how much we trained on, etc.

\subsection{Trained Models}

Describe the different feature-subsets that we trained and why.

\subsection{System Performance}

How long each model took to train and how fast we can predict. Also discussion the hardware that was used to train and predict in terms of CPU speed, memory, etc.

\subsection{Evaluation}

A table of a bunch of awesome results. We should present results by model type (SVM, CRF, LIN) and feature set.

\subsection{Discussion}

Talk about what we saw in terms of which was the best feature set and model.

Be sure to include examples of cool cases where it caught a difficult label

Be sure to include FAILURE cases

\section{Conclusion and Future Work}

I don't know, BS something...

\section{Acknowledgments}
